Faithful Model Explanations through\\ Energy-Constrained Conformal Counterfactuals

### 2023-12-14 paper/camera-ready/altmeyer.tex
done

Some of the members of TU Delft were partially funded by ICAI AI for Fintech Research, an ING---TU Delft
collaboration. Research reported in this work was partially or completely facilitated by computational resources and support of the DelftBlue~\citep{DHPC2022} and the Delft AI Cluster (DAIC: https://doc.daic.tudelft.nl/) at TU Delft. Detailed information about the utilized computing resources can be found in the appendix. The authors would like to thank Azza Ahmed, in particular, for her tremendous help with running Julia jobs on the cluster. The work remains the sole responsibility of the authors.

>>>>

Some of the members of TU Delft were partially funded by ICAI AI for Fintech Research, an ING---TU Delft
collaboration.

Research reported in this work was partially or completely facilitated by computational resources and support of the DelftBlue~\citep{DHPC2022} and the Delft AI Cluster (DAIC: https://doc.daic.tudelft.nl/) at TU Delft. Detailed information about the utilized computing resources can be found in the appendix. The authors would like to thank Azza Ahmed, in particular, for her tremendous help with running Julia jobs on the cluster. The work remains the sole responsibility of the authors.

Patrick would also like to express his gratitude to the group of students who have recently contributed to the development of CounterfactualExplanations.jl~\citep{altmeyer2023explaining}, the Julia package that was used for this analysis: Rauno Arike, Simon Kasdorp, Lauri Kesküll, Mariusz Kicior, Vincent Pikand.
